### 2015-08-10 evaluation.tex
fixes

\noindent\textbf{Experimental Setup }
%
We performed all experiments on a 3.40GHz Intel Core i7-2600 CPU with 16GB RAM running Ubuntu Linux 12.04.5 LTS, LLVM 3.5, SMACK 1.5.0, Z3~4.3.2, Boogie rev. 4192 and \corral rev. 534. We also used Mono~4.1.0 to run Boogie and \corral.

@@

\noindent\textbf{Race-Checking }
%
Table~\ref{tab:stats} presents statistics for our benchmarks: lines of code (LoC); number of possible entry point pairs (\#Pairs); number of SMACK memory regions (\#MRs); number of racy pairs (\#Racy Pairs) and number of racy memory regions (\#Racy MRs) reported by \whoop; and number of data races discovered by \corral using a context-switch bound (csb) of 2 (\#Races Found).\footnote{The number of racy memory regions can be less than the number of races found by \corral: \whoop might find that a memory region is racy, but the same memory region might race in several program statements.} Using a higher csb did not uncover any further races; this might mean that all races in our benchmarks can manifest with a csb of 2, or that \corral hit its recursion depth bound before discovering a deeper bug.

@@

\noindent\textbf{Accelerating \corral }
%
Table~\ref{tab:results} presents runtime results from using \whoop, \corral, and \whoop + \corral to analyze our benchmarks, while Fig.~\ref{fig:plot} plots the runtime speedups that \corral achieves using \whoop with the \yieldmr instrumentation. All reported times are in seconds and averaged over three runs. \corral was configured with a time budget of 10 hours (T.O. denotes timeout) and a csb of 2, 5, and 9. Standalone \corral uses \yieldall, which instruments context-switches (i.e. \texttt{yield} statements) after all visible operations, while \whoop + \corral uses \yieldcoarse and \yieldmr, which instrument context-switches in a more fine-grained fashion (see \S\ref{corral}). The table also shows the number of context-switches per instrumentation (\#Y).

>>>>

\noindent\textbf{Experimental Setup }
%
We performed all experiments on a 3.40GHz Intel Core i7-2600 CPU with 16GB RAM running Ubuntu Linux 12.04.5 LTS, LLVM 3.5, SMACK 1.5.0, Z3~4.3.2, Boogie rev. 4192 and \corral rev. 534. We also used Mono~4.1.0 to run Boogie and \corral. We configured \corral with a time budget of 10 hours (T.O. denotes timeout), a context-switch bound (csb) of 2, 5, and 9, and the default recursion depth bound of 1.

@@

\noindent\textbf{Race-Checking }
%
Table~\ref{tab:stats} presents statistics for our benchmarks: lines of code (LoC); number of possible entry point pairs (\#Pairs); number of SMACK memory regions (\#MRs); number of racy pairs (\#Racy Pairs) and number of racy memory regions (\#Racy MRs) reported by \whoop; and number of data races discovered by \corral using a csb of 2 (\#Races Found).\footnote{The number of racy memory regions can be less than the number of races found by \corral: \whoop might find that a memory region is racy, but the same memory region might race in several program statements.} Using a higher csb than 2 did not uncover any further races; this might mean that all races in our benchmarks can manifest with a csb of 2, or that \corral hit its recursion depth bound before discovering a deeper bug. We experimented with higher recursion depth bounds, but we were unable to discoverer any races that could not be found with the default one.

@@

\noindent\textbf{Accelerating \corral }
%
Table~\ref{tab:results} presents runtime results from using \whoop, standalone \corral, and \whoop + \corral to analyze our benchmarks, while Fig.~\ref{fig:plot} plots the runtime speedups that \corral achieves using \whoop with the \yieldmr instrumentation. Standalone \corral uses \yieldall, which instruments context-switches (i.e. \texttt{yield} statements) after all visible operations, while \whoop + \corral uses \yieldcoarse and \yieldmr, which instrument context-switches in a more fine-grained fashion (see \S\ref{corral}). The table also shows the number of context-switches per instrumentation (\#Y). All reported times are in seconds and averaged over three runs.
